Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-02-27 main.tex
add draft abstract

\begin{abstract}
\end{abstract}
\noindent\textbf{Index Terms}: speech recognition, feature extraction, raw waveform modeling

>>>>

\begin{abstract}
Raw waveform modeling is an interesting research topic for \gls{ASR}.
\wvtwo has seen large success recently and makes use of a convolutional \gls{FE} which operates directly on the speech waveform.
Typically, this \gls{FE} is seen as part of the overall architecture, but this work investigates this component specifically.
It is used as a replacement for classical feature extraction methods in a \gls{CTC} setup and compared to an alternative neural \gls{FE} approach.
Finally, we analyze the learned representations of both neural \glspl{FE}.
\end{abstract}
\noindent\textbf{Index Terms}: speech recognition, feature extraction, raw waveform modeling
